### 2014-11-11 report/preamble.tex
Use a macro to load CDF columns, position the legend closer to the inner edges

\pgfplotsset{datasetsCDF/.style=
{
xmin=0,
xmax=1,
ymin=0,
ymax=1,
grid=both,
xtick={0,.1,...,1.1},
ytick={0,.1,...,1.1},
enlargelimits=false,
% Marks 0% and 99%.
mark repeat=99,
legend pos=south east,
legend style={
cells={anchor=west},
},
},
datasetsCDFFullPage/.style=
{
width=\textwidth,
height=1.41\textwidth,
}
}

@@

>>>>

\pgfplotsset{datasetsCDF/.style=
{
xmin=0,
xmax=1,
ymin=0,
ymax=1,
grid=both,
xtick={0,.1,...,1.1},
ytick={0,.1,...,1.1},
enlargelimits=false,
% Marks 0% and 99%.
mark repeat=99,
% Using a custom position below.
% legend pos=south east,
legend style={
at={(.99,.01)},
anchor=south east,
cells={anchor=west},
},
},
datasetsCDFFullPage/.style=
{
width=\textwidth,
height=1.41\textwidth,
}
}

@@

\newcommand{\CDFPlotFromDataset}[3]{
	\addplot+[#3,solid,mark=*,every mark/.append style={#3,solid},]
		table[x=colnames,y=#2-http-www]
		{#1};
	\addlegendentry{#2-http-www}
	\addplot+[#3,dashed,mark=square*,every mark/.append style={#3,solid},]
		table[x=colnames,y=#2-https-www]
		{#1};
	\addlegendentry{#2-https-www}
}

\newcommand{\CDFPlotFromDefaultDatasets}[1]{
	\CDFPlotFromDataset{#1}{alexa.2014-09-01.top.10000}{red}
	\CDFPlotFromDataset{#1}{alexa.2014-09-01.top.se.10000}{blue}
	\CDFPlotFromDataset{#1}{se.2014-07-10.random.100000}{brown}
	\CDFPlotFromDataset{#1}{se.healthstatus.2013.municipalities}{violet}
	% \CDFPlotFromDataset{#1}{se.healthstatus.2013.media}{teal}
}

\newcommand{\CDFPlotFromDefaultDatasetsFile}[1]{
	\pgfplotstabletranspose[colnames from=Dataset]\tableTransposedDatasetsFromFile{#1}

	\CDFPlotFromDefaultDatasets{\tableTransposedDatasetsFromFile}
}
